Autocorrelation in Sparse Distributed Memory

### 2019-09-23 Chapters/sdm-autocorrelation.tex
init-paper-softwareX

Let $\Phi(x)$ be the cdf of the standard normal distribution. Let $z = \frac{r - n/2}{\sqrt{n}/2}$. $z$ is, hence, measuring the number of standard deviations from the average in the Gaussian, as $r$ varies\footnote{MARCELO, CHEQUE ESTA ULTIMA FRASE PLEASE?}.  Thus, $P(d(x, y) \le r) = \Phi(z)$. As $f = P(d(x, y) \le r)$, then, $f = \Phi(z)$ for our fixed $r$}.

>>>>

Let $\Phi(x)$ be the cdf of the standard normal distribution. If $z = \frac{r - n/2}{\sqrt{n}/2}$, $z$ is, hence, measuring the number of standard deviations from the average in the Gaussian\footnote{MARCELO, CHEQUE ESTA ULTIMA FRASE PLEASE?}.  Thus, $P(d(x, y) \le r) = \Phi(z)$. As $f = P(d(x, y) \le r)$, then, $f = \Phi(z)$ for our fixed $r$}.
